A meta-analysis of mental rotation ability in the first years of life

### 2022-04-21 code/analysis.Rmd
Code experiments with missing gender as "mixed"?

    # Convert gender to a categorical variable
    gender = case_when(
      female_percent == 1.0 ~ "female",
      female_percent == 0.0 ~ "male",
      !is.na(female_percent) ~ "mixed"
    ) %>% factor(levels = c("mixed", "female", "male")),

>>>>

    # Convert gender to a categorical variable
    gender = case_when(
      female_percent == 1.0 ~ "female",
      female_percent == 0.0 ~ "male",
      TRUE ~ "mixed"
    ) %>% factor(levels = c("mixed", "female", "male")),
